The effect of climate forcing on numerical simulations of the Cordilleran Ice Sheet at the Last Glacial Maximum

### 2013-11-20 sections/model.tex
Some small changes for homogeneity
Change geothermal reference (Irina)

The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}. SIA and SSA velocities are computed by finite difference methods on a 10\,km-resolution horizontal grid of 300 by 150 points (the modelling domain). Ice softness depends on temperature and water content through an enthalpy formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Enthalpy is computed in three dimensions in up to 51 irregularly spaced layers within the ice, and temperature is additionally computed in 11 regularly spaced layers in bedrock to a depth of 1\,km. A uniform geothermal heat flux of 70\,\unit{W\,m^{-2}} provides the lower boundary condition to the bedrock thermal model, and surface air temperature from the climate forcing provides the upper boundary condition to the ice enthalpy model.

@@

\subsection{Atmospheric corrections}

>>>>

The Shallow Shelf Approximation (SSA) is used as a ``sliding law'' for the Shallow Ice Approximation (SIA) \citep{bueler-brown-2009,winkelmann-etal-2011}. SIA and SSA velocities are computed by finite difference methods on a 10\,km-resolution horizontal grid of 300 by 150 points (the modelling domain). Ice softness depends on temperature and water content through an enthalpy formulation \citep{aschwanden-blatter-2009,aschwanden-etal-2012}. Enthalpy is computed in three dimensions in up to 51 irregularly spaced layers within the ice, and temperature is additionally computed in 11 regularly spaced layers in bedrock to a depth of 1\,km. A uniform geothermal heat flux of 70\,\unit{W\,m^{-2}}, characteristic of active tectonic margins on Earth \citep[e.g.,][]{artemieva-mooney-2001}, provides the lower boundary condition to the bedrock thermal model, and surface air temperature from the climate forcing provides the upper boundary condition to the ice enthalpy model.

@@

\subsection{Air temperature corrections}
